Analysis of Cartesian Genetic Programming's Evolutionary Mechanisms

### 2013-06-05 CGP Journal/main.tex
Added bar graphs and table

\begin{table*}
	\centering
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} &\graphicthird{multiply_skip_normal} & \graphicthird{multiply_skip_reorder} & \graphicthird{multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate}&\graphicthird{multiply_accumulate_normal} & \graphicthird{multiply_accumulate_reorder} & \graphicthird{multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single}&\graphicthird{multiply_single_normal} & \graphicthird{multiply_single_reorder} & \graphicthird{multiply_single_dag}\\ \hline
	\end{tabular}
	\caption{Location of never active nodes across all 50 runs for all nine algorithm combinations on the Multiply problem.}
	\label{tab:never_active}
\end{table*}

@@

\subsection{Node Behaviors}
TODO High amount of TF.

>>>>

\begin{table*}
	\centering
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    %\begin{comment}
    \thirdlabel{Skip} & \graphicthird{multiply_skip_normal} &
                        \graphicthird{multiply_skip_reorder} &
                        \graphicthird{multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{multiply_accumulate_normal} &
                              \graphicthird{multiply_accumulate_reorder} &
                              \graphicthird{multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{multiply_single_normal} &
                          \graphicthird{multiply_single_reorder} &
                          \graphicthird{multiply_single_dag}\\ \hline
    %\end{comment}
	\end{tabular}
	\caption{Location of never active nodes across all 50 runs for all nine algorithm combinations on the Multiply problem.}
	\label{tab:never_active}
\end{table*}

@@

\subsection{Node Behaviors}

\begin{table*}
	\centering
  \begin{tabular}{c|c|c|c|}
    \cline{2-4}
    & \textbf{\em Normal} & \textbf{\em Reorder} & \textbf{\em DAG} \\ \hline
    \thirdlabel{Skip} & \graphicthird{bar_multiply_skip_normal} &
                        \graphicthird{bar_multiply_skip_reorder} &
                        \graphicthird{bar_multiply_skip_dag}\\ \hline
    \thirdlabel{Accumulate} & \graphicthird{bar_multiply_accumulate_normal} &
                              \graphicthird{bar_multiply_accumulate_reorder} &
                              \graphicthird{bar_multiply_accumulate_dag}\\ \hline
    \thirdlabel{Single} & \graphicthird{bar_multiply_single_normal} &
                          \graphicthird{bar_multiply_single_reorder} &
                          \graphicthird{bar_multiply_single_dag}\\ \hline
	\end{tabular}
	\caption{Average node behavior for all nine algorithm combinations on the Multiply problem.
	         Excludes never active nodes.}
	\label{tab:behavior}
\end{table*}

Normal has the highest "used" bar unless its Single, likely because it also has the least active nodes

TODO High amount of TF.
